---
title: "HW10 Patrick Neyland"
author: "Patrick Neyland"
date: "11/22/2022"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Question 1
### 1
Ceteris paribus, if the number of cigarettes per day increases by 10, the birth weight will decrease by 4% on average. 

### 2
A white child is expected to weigh 5.5% more than a nonwhite child, on average holding all else constant. 
With a t-value of 4.23, yes—it is statistically significant. 

### 3
I don't think that the education of parents would be a great indicator of child birthweight. This feeling holds because $motheduc$ is not statistically significant. 

### 4 
The f statistic cannot be computed because the regressions use different samples. The regressions would have to be built using the same data to calculate the mentions F statistic


## Question 2
### 1
Yes, these is plenty of evidence to include $hsize^2$ in the model--it is statistically significant. From the equation, the optimal school size is one that has a graduating class of 4.41 hundred students. 

### 2
Holding hsize fixed, the difference between nonblack females and nonblack males is 45.09 points. With a 
t-stat close to 10, the difference is highly statistically significant. 

### 3
The estimated difference in SAT score between nonblack males and black males is 169.81 points. We reject the null hypothesis. 

### 4
The estimated difference in SAT score black females and nonblack females is 107.5 points. I would need to linearHypothesis test from R to test statistical significance. 

```{r include=FALSE}
library(wooldridge)
library(stargazer)
library(car)
```
## Question 3
### 1
```{r}
model6_1 <- lm(log(wage)~educ + exper + tenure + married +
                 black + south + urban, data = wage2)
stargazer(model6_1, type = "text")
```
Holding other factors fixed, on average, the approximate difference in monthly salary between blacks and nonblacks is 18.8%--with nonblacks being on the upper side of that difference. This difference is statistically significant. 

### 2
```{r}
model6_2 <- lm(log(wage)~educ + exper + I(exper^2) + tenure + I(tenure^2) + 
               + married + black + south + urban, data = wage2)
stargazer(model6_2, type = "text")
linearHypothesis(model6_2, c("I(exper^2)", "I(tenure^2)"))
```
They are not jointly significant even at 20%

### Part 3
```{r}
model6_3 <- lm(log(wage)~educ + exper + tenure + married +
                 black + south + urban + educ:black, data = wage2)
stargazer(model6_3, type = "text")
```
Because the coefficient of $educ:black$ is not significant, we can see that the return to 
education does not depend on race. 

```{r}
model6_4 <- lm(log(wage)~educ+exper+tenure+south+urban+I(married*(1-black))
               +I((1-married)*black)+I((1-married)*(1-black)), wage2)
stargazer(model6_4, type = "text")
```
The estimated wage differential between married blacks and married nonblacks is 17.9%
