---
title: "Homework 2"
author: "Patrick Neyland"
date: '2022-09-07'
output:
  word_document: default
  pdf_document: default
---
```{r include=FALSE,}
knitr::opts_chunk$set(
  comment = NA
)
library(wooldridge)
library(tidyverse)
# library(stargazer)
```

## Question 1
Replicate the following vector of numbers using seq() function and call it v1.
```{r}
v1 <- seq(1,17,4)
v1
```
## Question 2

### Part (I)
```{r comment=NA}
A <- matrix(seq(20,39,1), nrow = 4, ncol = 5, byrow = T)
A
```

### Part (II)
```{r comment=NA}
colnames(A) <- LETTERS[1:5]
A
```

### Part (III)
```{r comment=NA}
B <- A[c(2,4),c(2,4)]
B
```

### Part (IV)
```{r comment=NA}
B <- t(B)
B
```

### Part (V)
```{r comment=NA}
B_inverse <- solve(B)
B_inverse
```

### Part (VI)
```{r comment=NA}
round(B %*% B_inverse)
# Identity matrix
```

## Question 3
### Part (I) 
Assign the dataframe mtcars from the built-in datasets in R to a new dataframe
and call it df. Show the first 10 rows of your dataframs:
```{r , comment=NA}
df <- mtcars
head(df, 10)
```
### Part (II)
Make a new dataframe based on df and call it df1. Show the first 5 rows of df1.
```{r}
df1 <- df %>% select(c(cyl,hp,wt,vs,am,gear,mpg)) %>% arrange(cyl)
df1[1:5,]
```
### Part (III)
In df1 make a new column called gpm. Show the first 5 rows again.
```{r}
df1 <- df1 %>% mutate(df1,gpm = round(1/mpg,3))
head(df1, 5)
```
### Part (IV)
Show the structure of df1.
```{r}
str(df1)
```
### Part (V)
Change the type of the following variables (vs, am, cyl, gear) from num to
factor. Show the structure of df1 again.
```{r}
factors <- c('vs','am','cyl','gear')
df1[,factors] <- lapply(df1[,factors],factor)
str(df1)
```
## Question 4
### Part (I)
What is percentage of the men in the sample report abusing alcohol?
```{r comment=NA}
tb1 <- table(alcohol$abuse)
ptb1 <- prop.table(tb1)*100
ptb1[2]
```
### Part (II)
What is the employment rate?
```{r comment=NA}
df2 <- alcohol %>% filter(status != 1)
tb2 <- table(df2$status)
ptb2 <- prop.table(tb2)*100
ptb2[2]

```
### Part (III)
Consider the group of men who abuse alcohol. What is the employment rate?
```{r comment=NA}
df3 <- df2 %>% filter(abuse == 1)
tb3 <- table(df3$status)
ptb3 <- prop.table(tb3)*100
ptb3[2]
# Using a 2 variable prop.table makes this problem and the next
# a little more simple
tb6 <- table(df2$abuse, df2$status)
ptb6 <- prop.table(tb6,1)
ptb6
ptb6[2,2]*100
```


### Part (IV)
What is the employment rate for the group of men who do not abuse alcohol?
```{r comment=NA}
df4 <- df2 %>% filter(abuse != 1)
tb4 <- table(df4$status)
ptb4 <- prop.table(tb4)*100
ptb4[2]

# with prop table
ptb6[1,2]*100
```

### Part (V)
Discuss the difference in your answers to parts (III) and (IV). Does this allow you
to conclude that alcohol abuse causes unemployment?

No, you cannot conclude this causation because the causation may be in either direction. Causation may also be from other variables.  


