---
title: "HW3_Patrick Neyland"
author: "Patrick Neyland"
date: '2022-09-13'
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(comment = NA)
library(tidyverse)
```
# Appendix A
## Question 1
### Part i
```{r}
df <- c(300,440,350,1100,640,480,450,700,670,530)
avg_exp <- mean(df)
avg_exp
```
Average monthly expenditures is 566.

### Part ii
```{r}
med_exp <- median(df)
med_exp
```
Median monthly expenditures is 505.

### Part iii
```{r}
mean((df/100))
median((df/100))
```
They would each be divided by 100---becoming 5.66 and 6.05, respectively. 

### Part iv
```{r}
df[8] = 900
avg_exp2 <- mean(df)
avg_exp2
med_exp2 <- median(df)
med_exp2
```
The mean is increased by 20 while the median does not change. 


## Question 2
###
```{r}
.18-.15
(.18-.15)/.15
```
The majority shareholder considered the absolute change in percent return---.18-.15=.03
The CEO considered the relative change in percent return---.18-.15/.15=.2

## Question 3
### Part (i)

```{r}
salary <- function(exper) {exp(10.6+(0.027*exper))} 
salary(c(0,5))
```
The salary when $education=0$ is 40,134.84 while the salary when $exper=5$ is 45,935.80.

### Part (ii)
```{r}
dy <- function(dx){(100*0.027)*dx}
dy(5)
```
### Part (iii)
```{r}
((salary(5)-salary(0))/salary(0))*100
```
The estimator gives a change on 13.5 percent while the model has a change of 14.45 percent.

## Question 4
### Part (i)
```{r}
pnorm(6,5,sqrt(4), lower.tail = TRUE)
```
### Part (ii)
```{r}
pnorm(4,5,sqrt(4), lower.tail = FALSE)
```
### Part (iii)
```{r}
pnorm(4,mean= 5,sd = sqrt(4)) + (pnorm(6,mean = 5,sd = sqrt(4), lower.tail = FALSE))
```

## Question 5
```{r}
F <- function(x) {
 (3*(x^2))-(2*(x^3))
}
1-F(.6)
```
The probability that the elderly employment rate is at least 60 percent is 0.352

## Question 6 
```{r}
52.3*1000
14.6*1000
```
The mean and standard deviation are both just multiplied by 1,000. 
