---
title: "HW9 Patrick Neyland"
author: "Patrick Neyland"
date: '2022-11-01'
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, comment = NA)
```

## Question 1
### Part i
Take the first derivative with respect to sales, then set that equal to zero. $0.0003/0.00000014 = 21428.57$ this is when the marginal effect becomes zero. 


### Part ii
$H_0 \beta_{sales^2} = 0$
If alpha is greater than .069, then reject the null hypothesis. I will keep it because it is close to being significant in most cases. 



t = .000000007/.000000037 = 70/37
```{r}
70/37
pt(-1.891892, 29)*2
```
### Part iii

$\hat{rdintens} = 2.613 + 0.3salesbil - 0.000007salesbil$

error terms: 0.429, .14, 0.0000037

R^2 = 0.1484

### Part iv

I would prefer the latter model. It is easier to interpret and the $R^2$ stays the same. 

## Question 2

I would prefer the second model because it have the highest adjusted $R^2$

```{r}
library(wooldridge)
library(tidyverse)
library(stargazer)
```
## Question 3
### Part i

I expect it to be positive. As distance from the incinerator increases, price should also increase. 

### Part ii

```{r}
model3_2 <- lm(log(price)~log(dist)+log(intst)+log(area)+log(land)+rooms+baths+age, data = kielmc)
stargazer(model3_2 , type = "text")
```
The model shows that the distance from the incinerator does not have a significant effect on price. 

### Part iii

```{r}
lintst_squared <- (log(kielmc$intst))^2
model3_3 <- lm(log(price)~log(dist)+log(intst) + lintst_squared +log(area)+log(land)+rooms+baths+age, data = kielmc)
stargazer(model3_3 , type = "text")
```
The addition corrects the sign of log(dist) and makes all independent variables significant. 

### Part iv
Yes

## Question 4
### Part i
The model can be reparameterized:
$$y = \alpha_0 +\delta_1x_1 + \delta_2x_2 + \beta_3(x_1 - \mu_1)(x_2 - \mu_2)+u$$
Accoring to Wooldridge, we can show that
$$\delta_1 = \beta_1 + \beta_3exper$$


### Part ii



### Part iii



### Part iv
