---
title: "HW6 Patrick Neyland"
author: "Patrick Neyland"
date: '2022-10-11'
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(comment = NA, options(scipen = 999))
library(wooldridge)
library(stargazer)
library(tidyverse)
```

## Question 1

end of recording on 10/11 
### Part i
$\theta$ is unbiased. Expected value of theta hat is equal to theta hat. 
theta hat is equal to beta hat 1 + beta hat 2
E(theta hat) = E(beta hat 1 +beta hat 2)
= E(beta hat 1) E(beta hat 2)
= beta 1 + beta 2 = theta

### Part ii
going from cov to corr
Define unbiasedness

### Part ii


## Question 2

The bias will be negative because I think avg ability will be positive and the correlation between variables is negative. 



## Question 3
### Part i
Model 1 has df of 351
Model 2 has df of 350
Because SER is controlling for RBIS. less variance in sigma squared

### Part ii
Yeah, it makes sense. While having a little more experience can help someone have more RBIs, However

Variance inflation factor
VIF_year = 1/(1-R^2_year)
Cor(yr,rbiyr) = 0.487
R^2 = [Cor(yr,rbiyr)]^2
R^2 = 0.487^2
VIF_year = 1/(1-0.237)

```{r}
1/(1-0.237)
```

### Part iii
Because the signma squared are different. 

Square the SER to get Sigma^2

Because we are transition from the


## Question 5
### Part i
```{r}
model5_1 <- lm(math4 ~ pctsgle, data = meapsingle)
stargazer(model5_1, type = "text")
```
The effect of single parenthood seems large.

### Part ii
```{r}
model5_2 <- lm(math4 ~lmedinc + free, data = meapsingle)
stargazer(model5_2, type = "text")
```
It decreases significantly because other important variables are being controlled for. It seems that free lunch is a much better indicator of math scores.   

### Part iii
```{r}
cor(meapsingle$lmedinc,meapsingle$free)
```
The sample correlation between $lmedinc$ and $free$ is `r round(cor(meapsingle$lmedinc,meapsingle$free),4)`
Yes, it ahs the sign I expected. The higher a family's income, the less likely they will be to receive free lunch at school. 

### Part iv

I don't think the correlation between $lmedinc$ and $free$ are enough to justify dropping one of them on its own. The $R^2$ variable should also be considered. If we remove it without deeper analysis, we may be underspecifying the model and introducing unnecessary bias. 

### Part v
Watch class from 10/13 and look at the lecture R scripts

## Question 6
### Part i
```{r}
x <- range(htv$educ)
diff(x)
tb1 <- table(htv$educ==12)
ptb1 <- prop.table(tb1)*100
ptb1[2]
avg_educ <- round(mean(htv$educ),2)
avg_peduc <- round(mean(htv$motheduc + htv$fatheduc)/2,2)
```
The range of the $educ$ variable in the sample is `r diff(x)`.   
`r round(ptb1[2],2)` percent of men completed the twelfth grade but no higher.    
Average $educ$ is `r avg_educ` and the average parent education is `r avg_peduc`---on average, men have higher levels of education than their parents. 

### Part ii
```{r}
model6_2 <- lm(educ ~ motheduc + fatheduc, data = htv)
stargazer(model6_2, type = "text")
```
24.9 percent of the sample variation in $educ$ is explained by parents' education. Ceteris paribus, if $motheduc$ increases by 1 year, $educ$ will increase by 0.304 years on average.   
### Part iii
```{r}
model6_3 <- lm(educ ~ motheduc + fatheduc + abil, data = htv)
stargazer(model6_3, type = "text")
```
$\hat{educ} = 8.449 + 0.189\ motheduc + 0.111\ fatheduc + 0.502\ abil$
Yes, "ability" helps explain variations in education because it is relevant and not perfectly correlated with parents education. This is evidenced by the improve $R^2$ in part iii over the $R^2$ in part ii. 

### Part iv
```{r}
abil_squared <- htv$abil^2
model6_4 <- lm(educ ~ motheduc + fatheduc + abil + abil_squared, data = htv)
stargazer(model6_4, type = "text")
```
Leaving out other independent variables because they have no effect. 
$$\hat{educ} = 8.240 + 0.401\ abil + 0.051\ abil^2$$
$$\hat{educ}' = 0.401 + 0.102\ abil$$
Set $\hat{educ}$ equal to zero. 
$$0 = 0.401 + 0.102\ abil$$
$$ = \frac{-0.401}{0.102\ abil}$$
$abil^*$ is equal to `r round(-0.401/0.102, 2)`. $educ$ is minimized when $abil$ is `r round(-0.401/0.102, 2)`.
$$\hat{educ}'' = 0.102$$
Because the second derivative is positive, the critical value (`r round(-0.401/0.102, 2)`) is a minimum.

### Part v
```{r}
-0.401/0.102
tb2 <- table(htv$abil<(-0.401/0.102))
ptb2 <- prop.table(tb2)*100
ptb2[2]
```
From the data, only `r round(ptb2[2],2)` percent of men have an $abil$ less than -3.931.

### Part vi
```{r}
peduc_tot <- 12.18*.190 + .109*12.45
curve( peduc_tot + 0.401*x + 0.051*x^2, from=-4, to=7, n=500, 
       xlab="Ability", ylab="Years of Education", 
       col="blue", lwd=2, 
       main="Predicted Education based on Ability"  )
```

