---
title: "HW6 Patrick Neyland"
author: "Patrick Neyland"
date: '2022-10-11'
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(comments = NA, options(scipen = 999))
library(wooldridge)
library(stargazer)
library(tidyverse)
```

## Question 1

end of recording on 10/11 
### Part i
$\theta$ is unbiased. Expected value of theta hat is equal to theta hat. 
theta hat is equal to beta hat 1 + beta hat 2
E(theta hat) = E(beta hat 1 +beta hat 2)
= E(beta hat 1) E(beta hat 2)
= beta 1 + beta 2 = theta

### Part ii
going from cov to corr
Define unbiasedness

### Part ii


## Question 2

The bias will be negative because I think avg ability will be positive and the correlation between variables is negative. 



## Question 3
### Part i
Model 1 has df of 351
Model 2 has df of 350
Because SER is controlling for RBIS. less variance in sigma squared

### Part ii
Yeah, it makes sense. While having a little more experience can help someone have more RBIs, However

Variance inflation factor
VIF_year = 1/(1-R^2_year)
Cor(yr,rbiyr) = 0.487
R^2 = [Cor(yr,rbiyr)]^2
R^2 = 0.487^2
VIF_year = 1/(1-0.237)

```{r}
1/(1-0.237)
```

### Part iii
Because the signma squared are different. 

Square the SER to get Sigma^2

Because we are transition from the


## Question 5
### Part i
```{r}
model5_1 <- lm(math4 ~ pctsgle, data = meapsingle)
stargazer(model5_1, type = "text")
```
The effect of single parenthood seems large.

### Part ii
```{r}
model5_2 <- lm(math4 ~lmedinc + free, data = meapsingle)
stargazer(model5_2, type = "text")
```
It decreases significantly because other important variables are being controlled for. It seems that free lunch is a much better indicator of math scores.   

### Part iii
```{r}
cor(meapsingle$lmedinc,meapsingle$free)
```
The sample correlation between $lmedinc$ and $free$ is `r round(cor(meapsingle$lmedinc,meapsingle$free),4)`
Yes, it ahs the sign I expected. The higher a family's income, the less likely they will be to receive free lunch at school. 

### Part iv

I don't think the correlation between $lmedinc$ and $free$ are enough to justify dropping one of them on its own. The $R^2$ variable should also be considered. If we remove it without deeper analysis, we may be underspecifying the model and introducing unnecessary bias. 

### Part v
