---
title: "HW11 - Patrick Neyland"
author: "Patrick Neyland"
date: '2022-11-17'
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(comment = NA)

library(wooldridge)
library(tidyverse)
library(stargazer)
library(car)
```


## Question 1  
### Part 1
$$outlf = 1-0.586 + 0.0034nwifeinc - 0.038educ - 0.039 expr + 0.0006exper^2 + 0.016age + 0.262kidslt6 - 0.013 kidsage6$$
The coefficients will all switch signs and the new intercept will be 0.414

### Part 2
Standard errors will not change. 
### Part 3
No change in $R^2$



$$Var(ax+by$$
## Question 2
### Part 1

```{r}
df <- mutate(apple, ecobuy = ifelse(ecolbs>0, 1, 0 ))
sum(df$ecobuy)/length(df$ecobuy)

```
The fraction of families who claim they would buy ecolabeled apples is 62.4%

### Part 2
```{r}
MRM <- lm(ecobuy ~ ecoprc + regprc + faminc + hhsize + educ + age, df)
stargazer(MRM, digits = 4, type = "text")
```
$$\hat{ecobuy}=.424 -.803ecoprc + .719regprc + .001faminc + .024hhsize + .025educ - .001age$$
If ecoprc increases by 1 dollar, on average the likelihood of buying eco-labled apples decreases by 80.3 percent. If the regprc increases by 1 dollar, on average the likelihood of buying eco-labeled apples increases by 71.9 percent. 

### Part 3
```{r}
linearHypothesis(MRM, c("faminc=0", "hhsize=0", "educ = 0", "age = 0"))
```
With a p-value of 0.0015, the non-price variables are jointly significant. Looking at the model, the $educ$ variable seems to have the most important effect. This makes sense to me, someone with more education may be more informed on the importance of purchasing and consuming eco-friendly produce. However, $educ$ also acts as proxy variable for other variables that are also more significant. 

### Part 4
```{r}
MRM_log <- lm(ecobuy ~ ecoprc + regprc + log(faminc) + hhsize + educ + age, df)
stargazer(MRM,MRM_log,  digits = 4, type = "text")
```
The log model has a slightly higher adjusted $R^2$ however, because the two different variables between the models are not statistically significant, I would say the models are about the same. In the second model, as faminc increases by 1 percent, ecobuy will increase by 0.00045.

### Part 5
```{r}
sum(predict(MRM_log)<0)
sum(predict(MRM_log)>1)

summary(predict(MRM_log))
```
0 are negative and only 2 are above 1. We do not need to be concerned. 

### Part 6

```{r}
confusion_matrix <- table(df$ecobuy, predict(MRM_log) >= 0.5)
confusion_matrix
```
ecobuy = 0 | 102/(102+146) = .411 or 41.1%
ecobuy = 1 | 340/(72+340) = .825 or 82.5% (better)
Predicted correctly | (102 + 340)/(102+146+72+340) = 0.669 or 66.9%
The ecobuy = 1 model does a better job of predicting the decision to buy eco-labeled apples. 
