---
title: "HW12 Patrick Neyland"
author: "Patrick Neyland"
date: "12/6/2022"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## Question 1
Statements 2 and 3 are consequences. 

## Question 2
$\frac{beer}{inc} = \beta_0 + \beta_1inc + \beta_2price + \beta_3educ + \beta_4female$

y* = 

$\sqrt(h(inc)) = sqrt(inc^2) = inc$

divide everything by income. 

## Question 3
False

## Question 4
### Part 1
numerator df = k+1
denominator df = n-k-2

### Part 2
Because there are more explanatory variables on the right-hand side.


### Part 3
F depends on 3 things-- R^2\hatu^2, n, k


### Part 4
$\hat{u}

Something is wrong. Because \haty is a perfect linear combination of all x variables. This presents perfect colinearity. 

```{r}
library(wooldridge)
library(stargazer)

```

## Question 5

### Part 1
$$Var(u|male) = \delta_0 + \delta_1male$$
### Part 2
```{r}
model5_2 <- lm(sleep~ totwrk + educ + age + I(age^2) +yngkid + male, sleep75)
stargazer(model5_2, type = "text")


u_hat <- resid(model5_2)

reg_var <- lm(I(u_hat^2) ~ male, sleep75)

stargazer(reg_var, type = "text")
```
### Part 3
It was higher for women but it was not significant. 

## Question 6
### Part 1
```{r}

```

## Question 7
```{r}

```

## Question 8
```{r}
lm(e401k ~ inc + I(inc^2) + age + I(age^2) + male, k401ksubs)
```

